Additional analysis

### 2019-03-10 README.Rmd
Add OSF DOI

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "The effect of NGO crackdowns on individual philanthropy"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2019"
```

# The effect of NGO crackdowns on individual philanthropy

@@

> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://doi.org/xxx/xxx>

@@

> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://doi.org/xxx/xxx>

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

Title <- "The effect of NGO crackdowns on individual philanthropy"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2019"
```

# `r Title`

@@

> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org/10.17605/OSF.IO/FG53W>

@@

> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org/10.17605/OSF.IO/FG53W>
